Project 2

### 2021-10-12 project_2.Rmd
clean up code

```{r adding_female_words}
#collection of words representing a female
female_words <- c("she", "her", "woman", "girl", "aunt", "mother", "sister", "wife", "lady")

female_df <- tibble(word = female_words, female = TRUE)
```

```{r hemingway_tagged}
hemingway_tagged <- tidy_hemingway %>% left_join(female_df)
```

```{r fitzgerald_tagged}
fitzgerald_tagged <- tidy_fitzgerald %>% left_join(female_df)
```

```{r fitzgerald_count}
#counting how often female words appeared
#table shows each text and the respective percentage
fitzgerald_table <- fitzgerald_tagged %>% group_by(title) %>% count(female) %>% mutate(percent = n/sum(n)*100)

```{r hemingway_count}
#counting how often female words appeared
#table shows each text and the respective percentage
hemingway_table <- hemingway_tagged %>% group_by(title) %>% count(female) %>% mutate(percent = n/sum(n)*100)

```{r combined_result}
#table showing two authors and their respective usage of female words
author_table <- bind_rows(fitzgerald_tagged, hemingway_tagged)
author_table <- author_table %>% group_by(author) %>% count(female) %>% mutate(percent = n/sum(n)*100) %>% drop_na(female)

#table showing all texts and their respective usage of female words
combined_table <- bind_rows(hemingway_table, fitzgerald_table) %>% drop_na(female)
```
```{r frequency_distribution}
hemingway_wordcount <- tidy_hemingway %>% count(word, sort = TRUE) %>% mutate(frequency = (n/sum(n)), .after = n)
fitzgerald_wordcount <- tidy_fitzgerald %>% count(word, sort = TRUE) %>% mutate(frequency = (n/sum(n)), .after = n)

@@

## Sentiment Analysis

```{r all_author_sentences}
all_authors_sentence <- all_authors %>%
  group_by(author, title, text) %>%
  summarise (text = paste(text, collapse = "")) %>%
  unnest_regex(sentences, text, pattern = "[.?!]", to_lower = TRUE)  
```

```{r author_sentence_nr}
author_sentence_nr <- all_authors_sentence %>%
  ungroup() %>%
  mutate(sentence_number = row_number()) %>%
  group_by(author, title, sentence_number) %>%
  unnest_tokens(word, sentences) %>%
  anti_join(stop_words)
```

```{r author_concept}
author_concept <-  author_sentence_nr #%>%
  #left_join(emotion_words) 
```

```{r author_concept_sentiment}
author_concept_sentiment <- author_concept %>%
  inner_join(get_sentiments("bing"))
```

```{r author_sentiment_total}
author_sentiment_total <- author_concept_sentiment %>%
  count(sentence_number, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0)  %>%
  mutate(sentiment = positive - negative) #%>%
  #left_join(author_concept) #%>%
  #filter(emotion == TRUE)
```

```{r author_sentiment_table}
author_sentiment_table <- author_sentiment_total %>%
  #pivot_longer(sentiment,
               #names_to = "word",
               #values_to = "total_sentiment")  %>%
  #drop_na() %>%
  group_by(title, author) %>%
  summarise (total = sum(sentiment)) %>%
  ungroup()
```

```{r author_sentiment_plot}
author_sentiment_table %>%
  ggplot(aes(title, y = total, fill = title)) +
  geom_col(color = "black",
           alpha = .7,
           position = "identity") +
  #facet_wrap(~ concept) +
  labs(title = "Positive and Negative Sentiment by Concept",
       x = "Overal Sentiment",
       y = "Author",
       fill = "Title") +
  coord_flip() 
```

```{r exporting_tables}
save(author_table, hemingway_corpus, file = "saved_data.rda")
```

>>>>

```{r sentiment_nrc}
nrc_list <- get_sentiments("nrc")
counter <- tidy_hemingway %>% inner_join(nrc_list) %>% count(word, sort = TRUE)
sentiment_abs_h <- tidy_hemingway %>% inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("anger", 
                                         "anticipation", "disgust", "fear", "joy", "sadness", "surprise", "trust"))
    ) %>%
  count(sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% mutate(author = "Hemingway")#%>% 
  #mutate(sentiment = positive - negative)
total_words_hemingway <- NROW(tidy_hemingway)
sentiment_rel_h <- sentiment_abs_h[,-9]/total_words_hemingway
sentiment_rel_h <- sentiment_rel_h*100
sentiment_rel_h <- sentiment_rel_h %>% mutate(author = "Hemingway")
#anger	anticipation	disgust	fear	joy	sadness	surprise	trust
```

```{r}
nrc_joy <- get_sentiments("nrc")
#tidy_hemingway %>% inner_join(nrc_list) %>% count(word, sort = TRUE)
sentiment_abs_f <- tidy_fitzgerald %>% inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("anger", 
                                         "anticipation", "disgust", "fear", "joy", "sadness", "surprise", "trust"))
    ) %>%
  count(sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% mutate(author = "Fitzgerald")

total_words_fitzgerald <- NROW(tidy_fitzgerald)
sentiment_rel_f <- sentiment_abs_f[,-9]/total_words_fitzgerald
sentiment_rel_f <- sentiment_rel_f*100
sentiment_rel_f <- sentiment_rel_f %>% mutate(author = "Fitzgerald")
```

```{r}
sentiment_both <- bind_rows(sentiment_rel_h, sentiment_rel_f)

ggRadar(
  data = sentiment_both,
  mapping = aes(color = author),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```

@@

```{r exporting_tables}
save(author_table, hemingway_corpus, fitzgerald_corpus, file = "saved_data.rda")
```
